A Comparison of Graph Processing Systems

### 2020-09-23 documentation/paper/sections/discussion.tex

But not only distributed production systems are possible, of course. 
For small graphs, i.e. those that are not too large for single node RAM, a single-node setup is usually faster than the same framework on a distributed cluster. 
We have shown that the distributed cluster of the same framework becomes faster than the equivalent single-node setup only on large graphs.
We have found around 2B edges, or roughly the size of the twitter graph to be a size at which Ligra and Giraph are faster on the distributed setup compared to single-node.
If required, horizontal scaling can for example be used to provide fault-tolerance of the entire system.

@@

%## research
For single-node research systems, a overall good execution time on \emph{any} application is necessary. 
Here we recommend Galois as the fastest executing single-node framework overall.
It provides excellent performance, being orders of magnitude faster than the competing frameworks. And when it is possible to use hugepages, further improvements in performance can be expected. We frequently observed Galois with hugepages to be around 2 times faster compared to Galois without hugepages.
Also, we have shown that most algorithms are able to utilize many threads in favour of much smaller calculation times. Graph-traversal algorithms like BFS or SSSP shown here are examples for such algorithms.
Supplying a large thread pool for Galois is most likely improving performance on those algorithms.
However, especially when using push-style algorithms, a large thread count is most likely not going to significantly improve performance over single threaded results. 
The reason for this is the synchronization required for push applications. This is true not only for single-node Galois but any framework.

>>>>

But not only distributed production systems are possible, of course. 
For small graphs, i.e. those that are not too large for single node RAM, a single-node setup is usually faster than the same framework on a distributed cluster. 
We have shown that the distributed cluster of the same framework becomes faster than the equivalent single-node setup only on large graphs.
We have found around 2B edges, or roughly the size of the twitter graph to be a size at which Gemini and Giraph are faster on the distributed setup compared to single-node.
If required, horizontal scaling can for example be used to provide fault-tolerance of the entire system.

@@

%## research
For single-node research systems, a overall good execution time on \emph{any} application is necessary. 
Here we recommend Galois as the fastest executing single-node framework overall.
It provides excellent performance, being orders of magnitude faster than any of the competing frameworks. And when it is possible to use hugepages, further improvements in performance can be expected. We frequently observed Galois with hugepages to be around 2 times faster compared to Galois without hugepages.
Also, we have shown that most algorithms are able to utilize many threads in favour of much smaller calculation times. Graph-traversal algorithms like BFS or SSSP shown here are examples for such algorithms.
Supplying a large thread pool for Galois is most likely improving performance on those algorithms.
However, especially when using push-style algorithms, a large thread count is most likely not going to significantly improve performance over single threaded results. 
The reason for this is the synchronization required for push applications. This is true not only for single-node Galois but any framework.
